\documentclass[11pt]{article}
\usepackage{url,amsmath,setspace,amssymb,fullpage,color,varwidth,mdframed,mathtools}
\usepackage{enumitem}

\newcommand{\heading}[5]{
   \renewcommand{\thepage}{#1-\arabic{page}}
   \noindent
   \begin{center}
   \framebox[\textwidth]{
     \begin{minipage}{0.9\textwidth} \onehalfspacing
       {\bf CS 601.442/642 -- Modern Cryptography} \hfill #2

       {\centering \Large #5

       }\medskip

       {\it #3 \hfill #4}
     \end{minipage}
   }
   \end{center}
}

\newcommand{\scribe}[4]{\heading{#1}{#2}{}{ #4}{ #3}}

\newcommand{\proof}{{\bf Proof. }} %% To begin a proof write \proof
\newcommand{\qed}{\mbox{}\hspace*{\fill}\nolinebreak\mbox{$\rule{0.6em}{0.6em}$}} %%to end your proof write $\qed$.
\newcommand{\ma}{{\mathcal A}}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}
\bibliographystyle{plain}

\begin{document}
\scribe{1}{Instructor:
Abhishek Jain}{Homework 2}{Deadline: September 28; 2022, 1:30PM EST}


\section{Negligible Functions}
\begin{enumerate}[label=(\alph*)]
    \item (10 points) Prove that $2^{-\omega(\log n)}$ is a negligible function for any $n\in \mathbb{N}$.
    \item (10 points) Give an example $f$ and $g$ which are both negligible, but where $f(n)/g(n)$ is not negligible.
\end{enumerate}

\section{Hybrid Lemma}
\begin{itemize}[label=]
    \item (10 points) For integers $a\leq b$, let $U_{a,b}$ denote the uniform distribution over the integers $x$, $a\leq x\leq b.$ Now consider the following two distributions:
    \begin{enumerate}
        \item $U_{0,2^n-1}$
        \item $U_{2^n,2^{n+1}-1}$
    \end{enumerate}
    Consider the following proof via hybrid argument to establish that $U_{0,2^n-1}$ and $U_{2^n,2^{n+1}-1}$ are indistinguishable: 
For $0\leq i\leq 2^n,$ let $H_i=U_{i,2^n-1+i}.$ Clearly, $H_0=U_{0,2^n-1}$ and $H_{2^n}=U_{2^n,2^{n+1}-1}.$ Also, for every $i,$ $H_i\approx H_{i+1}$ because they are statistically close. Therefore, $U_{0,2^n-1} \approx U_{2^n,2^{n+1}-1}$. 

Is the above a valid proof? Explain your answer.   
\end{itemize} 
    
\section{Pseudorandom Generators}

\begin{enumerate}[label=(\alph*)]
\item (10 points) Let $G_1$ and $G_2$ be PRGs. Is $G(s)=G_1(s)||G_2(s)$ also a PRG? Prove or give a counterexample.
\item (10 points) Let $G:\{0,1\}^n\to\{0,1\}^{2n}$ be a PRG. Consider a function $H:\{0,1\}^n\to\{0,1\}^{4n}$ that works as follows:
$$
H(s): \text{First compute } s_1||s_2\coloneqq G(s) \text{, then compute and output } G(s_1)||G(s_2)  
$$
Is $H(\cdot)$ also a PRG? Prove or give a counterexample.
\item (15 points) Let $G:\{0,1\}^n\to\{0,1\}^{3n}$ be a PRG. Consider a function $H:\{0,1\}^{2n}\to\{0,1\}^{4n}$ that works as follows:
$$
H(s_1||s_2): \text{First compute } x\coloneqq G(s_2) \text{, then output } s_1||x 
$$

Prove \textbf{via reduction} that $H(\cdot)$ is also a PRG.

\end{enumerate}

\section{One-Way Functions}
Let $f: \{0,1\}^n \rightarrow \{0,1\}^n$ be any one-way function. Prove via reduction or disprove (by building an efficient inverter) each of the following statements.
    \begin{enumerate}
        \item (10 Points) Can a function that leaks some bits of the input still be a OWF? More precisely, let $f': \{0,1\}^{2n} \rightarrow \{0,1\}^{2n}$ be s.t. for every $x_1||x_2 \in\{0,1\}^{2n}$, $|x_1|=|x_2|$,\\ $f'(x_1||x_2)=f(x_1)||x_2$. Then is $f'$ also a one-way function?
         \item (10 Points) Let $f': \{0,1\}^{2n} \rightarrow \{0,1\}^{n}$ be s.t. for every $x_1||x_2 \in\{0,1\}^{2n}$, $|x_1|=|x_2|$,\\ $f'(x_1||x_2)=f(x_1)\oplus x_2$. Then $f'$ is also a one-way function.
    \end{enumerate}


\end{document}

